Current and future constraints on primordial magnetic fields

### 2016-10-21 pmf.tex
a

>>>>

A third question is whether it is better to integrate deeply on a small patch of sky or observe a wide area. 
As shown in  Fig.~\ref{fig:area}, it is better to go as wide as possible. 
A caveat to this analysis is that it is likely easier to remove galactic foregrounds to a specified level on targeted, `clean' patches as opposed to a substantial fraction of the sky, and we would expect galactic foregrounds to be important for the large angular scales. 
With that said, the PMF constraints improve rapidly with sky area up to XX \sqdeg, and improve by another XX\% up to the 70\% of the sky (the widest area likely to be possible after galactic cuts).
